A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-01-10 doc/large_strain.tex
minor

{\color{red}
Figure \ref{fig:roofline} shows the Roofline performance model.
As expected, the matrix-based approach is memory bound and (on average) achieves the performance of $8.5\,\rm{GFlop/s}$.
Matrix-free implementation of fine-strain elastic tangent operators (on average) leads to a much better performance of
$22.6\,\rm{GFlop/s}$, as well as about an order of magnitude higher computational intensity, but still stays in the memory bound regime.
The achieved performance is about 13\% of the peak arithmetic performance, which is considerably lower than the
70\% reported for the Laplace operation in \cite{kronbichler12}.
When comparing the data for ``tensor4'' caching strategy (Algorithm \ref{alg:mf_tensor4}) to that from the ``tensor2'' (Algorithm \ref{alg:mf_tensor2}),
we observe very marginal increase in computational intensity and almost unchanged performance.
This indicates the origin for suboptimal results of matrix-free approach is most likely not related to the algorithms studied here.
Further detailed studies are necessary to explain this behavior.
}

>>>>

{\color{red}
Figure \ref{fig:roofline} shows the Roofline performance model.
As expected, the matrix-based approach is memory bound and (on average) achieves the performance of $8.5\,\rm{GFlop/s}$ (4.5\% of the peak performance).
Matrix-free implementation of fine-strain elastic tangent operators (on average) leads to a much better performance of
$22.6\,\rm{GFlop/s}$, as well as about an order of magnitude higher computational intensity, but still stays in the memory bound regime.
The achieved performance is about 13\% of the peak arithmetic performance, which is considerably lower than the
70\% reported for the Laplace operation in \cite{kronbichler12}.
When comparing the data for ``tensor4'' caching strategy (Algorithm \ref{alg:mf_tensor4}) to that from the ``tensor2'' (Algorithm \ref{alg:mf_tensor2}),
we observe very marginal increase in computational intensity and almost unchanged performance.
This indicates that the origin for suboptimal results of matrix-free approach is most likely not related to the algorithms numerically investigated here.
Further detailed studies are necessary to explain this behavior.
}
